---
title: "ISMB2019 Usage"
author: "Venu Thatikonda" 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ISMBECCB2019-CONFERENCE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Package helps retreiving tweets that were tweeted during a specific talk from ISMB/ECCB 2019 conference. Given a date, start and end time of a particular talk, the following code extracts tweets in that time slot.

I hope this package will help people who did not attend the conference and people who attended but did not get the chance to listen to all talks.

At following links, one can find times of different talks from different COSI's

[https://www.iscb.org/ismbeccb2019-program/ismbeccb2019-cosi-other-abstracts](https://www.iscb.org/ismbeccb2019-program/ismbeccb2019-cosi-other-abstracts)


```{r setup}
library(ISMB2019)
library(magrittr)

data(ismb_dat2019)

## date
my_day <- "2019-07-24"

## start time of talk HH:MM
start_time <- "16:00"

## end time of talk HH:MM
end_time <- "17:00"

ISMB2019::get_tweets(my_day = my_day, start_time = start_time, end_time = end_time)

```
